Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-05-21 chapters/ch_experiment.tex
Routine upload

\begin{equation}\label{eq:gaus}
PRF_{\mathrm{Gaus}}(\lambda) = N_0 e^\frac{-\lambda^2}{2\sigma^2}
\end{equation}

@@

%\section{Collision Data Taken}

>>>>

\begin{equation}\label{eq:prfgaus}
PRF_{\mathrm{Gaus}}(\lambda) = N_0 e^\frac{-\lambda^2}{2\sigma^2}
\end{equation}

@@

\section{Collision Data Taken}

Shown in Fig.~\ref{fig:cocktail} is a typical cocktail event, where one particle enters the TPC volume at a time and parallel to the pad plane, representing an ideal case for momentum and $dE/dx$ determination; as it does not suffer from inefficiencies of high multiplicity events seen in the collision experimental data.  tb

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{cocktail.png}
\caption{Pad plane projection for a cocktail event in the TPC.}
\label{fig:cocktail}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{data.png}
\caption{Pad plane projection for a collision event in the TPC. Highlighted by red arrows are two regions of anode wires which had a reduced voltage of 1214 V. The voltage of the rest of the TPC anode wires are 1460 V. The reduction in voltage reduces the gain by a factor of about 10. }
\label{fig:data}
\end{figure}
